Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-18 cav2017/cav2017.tex
First version of safety specifications description

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback can be employed to affect the properties and behaviours of the process. 
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
The most basic feedback architecture is the state feedback, 
where the control action $\vec{u}_k$ is computed by: 
%
\begin{equation}
u_k = r_{k} - K x_k, 
\end{equation}
%
where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal.   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
according to a desired goal or objective. 
A standard objective is to obtain stable closed-loop dynamics.

@@

Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$, which is
given as a set of linear constraints over the inputs and outputs.

>>>>

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback can be employed to affect the properties and behaviours of the process. 
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
The most basic feedback architecture is the state feedback, 
where the control action $\vec{u}_k$ is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k, 
\end{equation}
%
where $K \in \mathbb{R}^{m \times n}$ is a feedback gain matrix, 
and $r_{k}$ is a reference signal.   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop dynamics are shaped as desired, 
according to a desired goal or objective. 
A standard objective is to obtain stable closed-loop dynamics.

@@

Finally, we also require that the closed-loop systems meets safety specifications. A safety specification establish bounds for the states, such that he controller $K$ must maintain the states within these bounds for any initial state.

The safety property (represented by $\phi_{safety}$) is encoded as follows:
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
where $x_{i}^{-}$ and $x_{i}^{+}$ are respectively the lower and upper bound of the $i$-th state $x_{i}$ at the $k$-th instant, i.e., the states will always be within the $n$-dimensional hyperbox defined by the safety specifications (bounds).

The closed-loop state-space system have to be unrolled until a specific depth ($k_{bound}$) to ensure $\phi_{safety}$. The limit $k_{bound}$ is the number of iterations sufficient so that the rate of variation (derivative) of the states is negligible ensuring the boundaries will not be violated for any $k>k_{bound}$. \commentib{The k-bound estimative must be explained.}

For any $k\leq k_{bound}$ the states must be computed considering the FWL effects in all operations related to the control action~\ref{eq:controlaction} and disregarding it in the state equation ~\eqref{eq:plant}. Thus, the states are computed using the following equations:
\begin{equation}
\label{eq:ssunroll}
\left\lbrace
\begin{array}{l}
u_{k}=\mathcal{F}_{\langle I,F \rangle}(r_{k}-\mathcal{F}_{\langle I,F \rangle}(\mathcal{F}_{\langle I,F \rangle}(K)\cdot\mathcal{F}_{\langle I,F \rangle}(x_{k})))\\
x_{k+1}=Ax_{k}+Bu_{k}
\end{array}\right.
\end{equation}
